\input{common.inc.tex}
\topic{Meeting 2}
\date{8th August, 2011}
\present{Rohit, Brian, John, Antriksh}
\apologies{Alwyn}
\absent{-}
\begin{document}

\maketitle{}

Meeting opened 10:00 AM

\section{Meeting Times}
\begin{itemize}
\item Need to select Mentor Meeting and Client Meeting times
\item Client meeting least important for everyone to attend
\item Who is mentor? When is avaiable?
\item Avaliable times - Monday 10AM \& 11AM, Wednesday 2PM \& 4PM
\end{itemize}

\section{Deliverable A}
\begin{itemize}
\item Discussion on who gets what section
 \begin{itemize}
 \item 1 - General Goals
 \actioned Rohit
 \item 2 - Current System
 \actioned John
 \item 3 - Proposed System [3.0-3.4]
 \actioned Brian
 \item 3.5.1 - Scenarios
 \actioned Alwyn
 \item 3.5.5 - User Interface
 \actioned Antriksh
 \item 4.0 - Glossary
 \actioned Everyone
 \end{itemize}
\end{itemize}

\section{Bookable Hours}
\begin{itemize}
\item Submit bookable hours by Thursday
 \begin{itemize}
 \item What if there is more work to do on Fri?
 \item Submit as late as possible, and if too late, just estimate instead
 \end{itemize}
\end{itemize}

\section{Client Requirements}
\begin{itemize}
\item{Requirements vs Wishlist}
 Ask the client what is needed, vs what would be ``nice''
 \begin{itemize}
 \item{Decided against a ``wishlist'' until Deliverable A is written}
 \end{itemize}
\item{Questions}
 \begin{enumerate}
 \item{What is the desired API?}
  How will he interface with the engine? Function Pointers, ...
 \item{What values/parameters?}
 \item{Special features - Multithreading, Async operation, ...}
 \item{What output format?}
 \item{Config for external functions? Do we init them, or do they init us?}
 \item{Environment? What will this be used for?}
 \item{Ease of Use, Generality, or speed?}
 Should we assume types of input value / genenome.
 \end{enumerate}
\end{itemize}

\nextmeeting{TBD}

\meetingclosed{10:46}

\end{document}
